---
title: "Homework_3"
author: "Sijay Matsinye"
date: "2/16/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1) Enter and run USArrests. What type of information is shown in the data table USArrests? (Three or four sentences)

    ** This data table shows the rates of arrests for three different types of violent crimes broken down by state. THe table includes four variable that are the three crimes: murder,assault, rape along with the percent of the population living in urban areas. Lastly the rate represented for each crime is calculated per every 100,000 residents.
```{r}
library(tidyverse)
USArrests
```

##2) Use and show R coding that features a map function to show maximum values for all variables of the USArerests data frame. Which State has the largest number of Assaults according to the USAressts data frame ?

    **North Carolina has the largest number of Assaults according to the USArrests data frame.
```{r}
map_dbl(USArrests, max)
USArrests %>% 
  arrange(desc(Assault))
```

##3) Install the nycflights13 package: install.packages("nycflights13"), call the following library:library(nycflights13), and then enter (this will produce the flights data table)
```{r}
#install.packages("nycflights13")
library(nycflights13)
flights
``` 

##4) Use and show R code that will indicate how many rows and how many columns the flights data has. Review and revisit your notes from STAT 412/612. Describe a tibble (two or three sentences).Now use and show R code that verifies that flights is a tibble

    **A tibble is a data frame that doesn't perform al of the actions of a data frame. When printed it only shows a preview of all the values and objects in the data frame and it can't change the object types. Overall it performs modified actions of that which a data frame does. 
```{r}
flights %>% 
  nrow()
flights %>% 
  ncol()
flights %>% 
  is_tibble()
```

##5)Now Use and show R code (featuring a map function) that will output the type of each column of the flights tibble.
```{r}
flights
map(flights,typeof)
```

##6)Use and show R coding that features usage of a map function to find the slope and the intercept of models for the different levels of the Species variable of the iris data frame. For each model, Sepal.Width predicts Sepal.Length.

```{r}
models <- iris %>%
  split(.$Species) %>%
  map(~lm(Sepal.Length ~ Sepal.Width, data = .))
models
```

7)
```{r}
V <- list(12, 22, 27, 31.5, NA, 39, "east")
V
```

7a) Use and show R code to find the length of the list
```{r}
length(V)
```



7b) Use and show R code that will extract the missing value
```{r}
V[is.na(V)]
```

7c) Use and show R code that will extract the third object
```{r}
V[3]
```

7d) Use and show R code that will extract the character string and the minimum number.
```{r}
str(V[1])
str(V[7])
```

7e) Use one line of code to show that the seventh object is a character object.
```{r}
str(V[[7]])
```
